A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-29 4_method.tex
dissipate theoretical analysis into Significance measure. Smooth transitions, and Computation time sections

%\subsubsection{Significance measure}\label{sec:significance_measure}
\paragraph{Significance measure}
We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}. 
An edge is significant if the bisector angle on any location on the edge exceeds a prescribed $\alpha_\text{max}$. 
As illustrated in See \cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$. This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
The bisector angle is therefore an exact indicator of the amount of overfill and underfill in the uniform toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.

@@

A sharp transition from $n$ to $n+1$ beads at an anchor location creates sharp turns in the toolpath (see \cref{transitions} top).
A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
The length of the transition is set to $t(n) = w^*$ and it is centered at the anchor, i.e. the distance from the lower end $v_0$ to the anchor position $v_x$ is set to
$t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$,
where $\Delta$ is the total distance along the edges in between two nodes.
We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
In order to make the transition ramps robust against small perturbations in the outline shape, we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $\hat{b}$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
\begin{equation}
\hat{b}_{v_x} = n + {\Delta(v_0v_x)} / {\Delta(v_0v_1)}
\end{equation}
%This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
%compare the top and bottom of \cref{beading_transitioning_filtering}. 
Finally we update the ST by adding support edges at the transition ends. 
As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w^*$ for long stretches with ramps in between.

>>>>

%\subsubsection{Significance measure}\label{sec:significance_measure}
\paragraph{Significance measure}
We make use of the \emph{bisector angle} as an indicator of significance which is commonly used in shape analysis.
%Centrality can be formalized by looking at a commonly used significance measure knows as the \emph{bisector angle}.
The bisector angle $\alpha$ is the interior angle $\angle{p_0lp_1} \leq \SI{180}{\degree}$, between any location $l$ on an edge of the ST and its two supporting points $ \{ p_0, p_1 \} = \text{sup}(l)$~\cite{attali1996modeling}. 
An edge is significant if the bisector angle on any location on the edge exceeds a prescribed $\alpha_\text{max}$. 
As illustrated in See \cref{naive_overfill_underfill}, for a polygon with a pointy wedge area of an angle $\beta$, we have $\alpha = 180\degree - \beta$. This corresponds to overfill areas and underfill areas the size of $\nicefrac12 (w^*)^2 \left( \nicefrac14 \tan ( \alpha / 2) - \alpha / 2 \right)$ when filled using the simple technique of uniform bead width $w^*$.
Although significance measures are commonly used as a heuristic for finding the parts of a skeleton which are in some sense relevant~\cite{attali1996modeling,Sud2007},
we use the bisector angle as an \emph{exact} indicator of the amount of overfill and underfill in the uniform toolpaths of constant width.
%Contrary to related literature we will \emph{keep} the non-significant regions of the skeleton.
%We mark all significant edges as such and contrary to related literature we keep the unmarked edges of the ST.

@@

A sharp transition from $n$ to $n+1$ beads at an anchor location creates sharp turns in the toolpath (see \cref{transitions} top).
A transition length $t(n)$ is introduced to ensure a smooth transition (see \cref{transitions}). 
The length of the transition is set to $t(n) = w^*$ and it is centered at the anchor, i.e. the distance from the lower end $v_0$ to the anchor position $v_x$ is set to
$t_0(n) = \Delta(v_0v_x) = \nicefrac12 w^*$,
where $\Delta$ is the total distance along the edges in between two nodes.
We discard any transition anchor which is too close to the end of a chain of marked edges for the smoothed transition to fully fit within the marked region.
In order to make the transition ramps robust against small perturbations in the outline shape which cause extra (support) edges in the skeleton,
we modify the nodes $v_x$ which are in between the two ends $v_0$ and $v_1$ of the transition by (re-)assigning them a fractional bead count $\hat{b}$ which is linearly interpolated between the two ends of the transition (see \cref{beading_transitioning_filtering__transitions_applied}):
\begin{equation}
\hat{b}_{v_x} = n + {\Delta(v_0v_x)} / {\Delta(v_0v_1)}
\end{equation}
Note that although the ST is not stable against noise in the boundary shape, the distance field itself is, so by designing our algorithms such that they are stable against changes in the topology of the skeleton our method is stable against small perturbations in the outline.
%This modification makes the transition ramps robust against small perturbations in the outline shape (to be explained in \cref{section_beading_interpolation});
%compare the top and bottom of \cref{beading_transitioning_filtering}. 
Finally we update the ST by adding support edges at the transition ends. 
As shown in \cref{beading_transitioning_filtering__result_uoc}, the marked regions in the UoC mesh have become horizontal at integer multiples of $\nicefrac12 w^*$ for long stretches with ramps in between.

### 2019-08-29 6_validation.tex
Tims edits to limitations and applications
dissipate theoretical analysis into Significance measure. Smooth transitions, and Computation time sections

\subsubsection{Computational performance}
\cref{computime} plots the computation time against the vertex count of the layer for the full data set, comparing the uniform technique~\cite{johnson2014clipper} to our framework with the inward distributed scheme.
For polygonal shapes with as many as $10^4$ vertices, the computation for both approaches is less than 1 second, with our method being approximately five times that of the uniform technique.

@@

The prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
The prints which employ the uniform offsets technique clearly show a lot of underfill, which clearly impacts the visual performance of the print.
Moreover, in the case of the regular honeycomb there are several disconnected hexagons, while the whole part is supposed to be a single connected solid.
The difference between the centered and the inward distributed schemes is less pronounced.
We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extremal bead widths.
The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.

>>>>

\subsubsection{Computational performance}
\cref{computime} plots the computation time against the vertex count of the layer for the full data set, comparing the uniform technique~\cite{johnson2014clipper} to our framework with the inward distributed scheme.
For polygonal shapes with as many as $10^4$ vertices, the computation for both approaches is less than 1 second, with our method being approximately five times that of the uniform technique.
These results could be improved upon by utilizing the locality inherent in our algorithms for parallelization on the GPU.

@@

The prints are shown in \cref{wedge_print} and \cref{prints}.
Because of inaccuracies in the deposition control system some of the prints show defects.
Such defects are less prevalent for the inward distributed beading scheme than the other schemes.
The prints which employ the uniform offsets technique clearly show a lot of underfill, which clearly impacts the visual quality of the print.
Moreover, in the case of the regular honeycomb there are several disconnected hexagons, while the whole part is supposed to be a single connected solid.
The difference between the centered and the inward distributed schemes is less pronounced.
We can still see some loosely connected extrusion segments in both, which is attributable to inaccuracies in the extrusion system.
However, the middle of \cref{wedge_print} exhibits more defects in the regions where the centered scheme produces extremal bead widths.
The bottom print shows that the inward distributed beading scheme produces smoother prints with less defects.
